Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-20 paper/paper.tex

For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios. Table~\ref{tab:test262} shows
\begin{wraptable}[10]{r}{0.22\textwidth}
  \vspace{-2ex}      
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \vspace{-2ex}        
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\    
    \smonkey{} & \percentSuiteTestSM{} \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-4ex}
\end{wraptable}
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}. Results show that there
are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was very
      effective at finding bugs in \js\ engines. 
      \end{minipage}
    }
\end{center}

@@

\begin{itemize}
  \item Both techniques investigated were successful in revealing
    bugs (several of them);
  %% \item We have found more bugs with test transplantation than we have
  %%   with cross-engine differential testing. In addition, test
  %%   transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs. We conjecture that there is room to find more
    bugs using other fuzzers;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we used, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}

The main lessons we learned in this study are the following: 1)~Even
for problems with fairly clear specifications, as in \javascript{},
there is likely to be (a lot of) variation between different
implementations. 2)~Not only multiple different implementations can be
leveraged in differential testing, but differences in test suites can
also be important. 3)~Differential testing is feasible on real,
complex, widely used pieces of software. 4)~The cost of inspecting
failures/warnings is high. Although the inspection activity was not
uninterrupted, it is safe to say that each warning required a
substantial amount of time to analyze for potential false alarms. We
prefer to see this as an opportunity for future research in applying
learning techniques to prioritize warnings more likely to be faulty.
%based on static and dynamic features.

>>>>

For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios. Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}. Results show that there
\begin{wraptable}[10]{r}{0.22\textwidth}
%  \vspace{-2ex}      
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \vspace{-2ex}        
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\    
    \smonkey{} & \percentSuiteTestSM{} \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-4ex}
\end{wraptable}
are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was
      effective at finding \js\ engines bugs, several of which have
      been fixed already.
      \end{minipage}
    }
\end{center}

@@

\begin{itemize}
  \item Both techniques we investigated were successful in revealing
    bugs (several of them);
  %% \item We have found more bugs with test transplantation than we have
  %%   with cross-engine differential testing. In addition, test
  %%   transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs. We conjecture that there is room to find more
    bugs using other fuzzers;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we used, with Google's \veight\ after it.
\end{itemize}

The main lessons we learned from this study are as follows: 1)~Even
for software projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
variation between different implementations and, therefore,
opportunities for bugs. 2)~Not only multiple different implementations
can be leveraged in differential testing, but differences in test
suites can also be important. 3)~Finding functional/non-crash bugs
with differential testing is feasible on real, complex, widely used
pieces of software. 4)~Further reducing cost of inspection is an
important problem. Although the inspection activity was not
uninterrupted, it is safe to say that each warning required a
substantial amount of time to analyze for potential false alarms. In
fact, many \hi\ warnings reported with differential testing were not
analyzed. In determining cost, we observed, from experience, that the
complexity of the \js\ specifications that the original test covers
increases cost of diagnosing (as developers need to read and
understand those) and the availability of alternative implementations
(for the cases warnings are revealed through differential testing)
reduces the cost of diagnosis. We prefer to see such problem as an
opportunity for future research. For example, applying learning
techniques to prioritize the warnings more likely to be faulty may be
a promising avenue to explore. Recall that most of those warnings are
false positives.  5)~We learned that reporting real bugs is a great
way to train (and encourage) students in software testing. Students
praised the experience of diagnosing failures, understanding part of
the specs (as needed), writing bug reports, participating in
discussions on issue trackers, and observing the change of
status. That was a relatively self-contained hands-on activity that
enabled students to engage in a real-life serious industrial project.
